\documentclass[uplatex,a4j,12pt,dvipdfmx]{jsarticle}
\usepackage{amsmath,amsthm,amssymb,bm,color,enumitem,mathrsfs,url,epic,eepic,ascmac,ulem,here,ascmac}
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}
\usepackage[english]{babel}
\usepackage[dvipdfm]{graphicx}
\usepackage[hypertex]{hyperref}

\title{Self-Defense Against Brainwashing (Reading Notes)}
\author{Masaru Okada}
\date{\today}

\begin{document}

\maketitle


\section{The Boundary Between Education and Brainwashing}

The fundamental purpose of education should be for \textbf{the benefit of the individual}, not for the benefit of a third party; from this perspective, education is distinct from brainwashing (p. 11). However, when taking a perspective that transcends national borders, careful scrutiny is essential to determine whether a country's education truly serves the individual's benefit or if it has become '\textbf{brainwashing}' for the benefit of a third party. The current educational system in North Korea, for instance, is often cited as a possible case of brainwashing from a global viewpoint (p. 11).

\section{The Danger Posed by 'What is Right'}

The core of the issue lies not in the correctness or incorrectness of a specific nation's ideology (e.g., Saddam Hussein's regime in Iraq or American democracy) but in a situation where \textbf{an overwhelming majority of citizens strongly believe in a specific 'right thing'} (p. 12). Even if American democracy is objectively more correct than North Korea's autocratic, militaristic state ideology, the fact that nearly all Americans strongly believe in that democracy is problematic (p. 12). The more correct a 'right thing' is perceived to be, and the higher the percentage of the population strongly believing in it, the stronger the impulse becomes to \textbf{thoroughly eliminate 'what is wrong'} (p. 13). Consequently, even actions that must be absolutely avoided, such as war, are excused, justified, and carried out brazenly (p. 13). The atomic bombings of Hiroshima and Nagasaki in the past may also have been justified under the pretext of 'stopping the runaway of an erroneous Imperial Japan' (p. 13).

\subsection*{The Centralization of Principle Interpretation Authority}

Even with a 'correct' philosophy, ideology, or religion, the overwhelming majority of citizens believing in it is dangerous because the \textbf{authority to interpret} that \textbf{principle} (the fundamental concept) and apply it to concrete situations becomes concentrated in a single political power (p. 14). Just as the interpretation of the Bible was once monopolized by the Pope in Christianity, a similar structure exists in contemporary America, where the President monopolizes the authority to interpret American democracy (p. 14). The Iraq War is an example that made it feel as if the President held the authority to interpret the Bible as well (p. 14). The fact that religions, which are inherently peaceful, such as Islam and Christianity, cause terrorism and war, is a result of the excessive concentration of the principle's interpretation authority in specific political powers, dating back to the Crusades (p. 14).

\section{Diversity for Averting War}

It is the unit that possesses military power—the nation-state—that makes the decision to wage or participate in war. Therefore, war cannot occur unless the state decides to engage (p. 18). To avoid the decision to participate in war, the solution lies in \textbf{avoiding a situation where virtually all citizens agree}—in other words, citizens must not share the same criteria for judgment but \textbf{believe in diverse values} (p. 18). It is hypothesized, for instance, that the Iraq War would not have occurred if 10\% of the American population had been Muslim (the actual figure is less than 0.3\%). The high ratio of Christians in America (85\%) is highlighted as a state of excessive adherence to a single religion (p. 18).

\section{Brainwashing Techniques and Self-De-brainwashing}

The author expresses the intention that, as a social responsibility, \textbf{transmitting the technique of self-de-brainwashing to all Japanese citizens} will prevent the entire populace from being bound by a single value, thereby contributing to the avoidance of war (p. 18).

\subsection*{Hereditary Politicians and Brand Consciousness in Japan}

About one-quarter of Japanese Diet members are hereditary, and an analysis suggests that hereditary candidates are an astonishing \textbf{10,000 times more advantageous} in elections compared to the children of ordinary families (p. 22). This situation is equivalent, in terms of population ratio, to Muslims in the US (less than 0.3\%) occupying a quarter of the US Congress, a profoundly imbalanced state (p. 22). This electoral advantage is argued to be an expression of the public's \textbf{brainwashed brand consciousness} (p. 22).

\subsection*{The Logic of 'The Other World' and 'This World'}

A person whose 'logic of the other world' is completely free from worldly desires transcends the social judgments of this world, making the terms good and evil meaningless (p. 24). A cynical view is presented: even if one achieves freedom from the 'logic of this world' through self-de-brainwashing, this \textbf{bears no relation to whether one is a good person} (p. 24). Since what is considered 'good' is itself a \textbf{social judgment} given by the ruling powers of the time, believing something to be good should be considered a result of being brainwashed (p. 24).

\subsection*{Definition of Brainwashing and De-brainwashing Technique}

\textbf{Brainwashing} is defined as 'controlling a person's thoughts, actions, and emotions as desired by applying some kind of intrusive manipulation to the internal information processing of the brain, including at the cognitive level, for \textbf{the benefit of a third party}' (p. 28). De-brainwashing is impossible simply by giving a cult member the information that they were 'deceived'; it requires \textbf{the technique to overwrite} the brain, which was written with manipulated information, \textbf{with different information} (p. 25). This book offers precisely this \textbf{self-de-brainwashing technique} (p. 25). A warning is also given that cults advocating vague, neatly packaged doctrines like 'world peace' or 'the future of the universe' are more dangerous, and the activities of well-known figures are also questioned (p. 29).

% \section{Universal Theory/Concepts}
% Brainwashing, Self-De-brainwashing, Principle, Centralization of Interpretation Authority, Diverse Values, Brainwashed Brand Consciousness, The Logic of the Other World, The Logic of This World

\subsection{Comprehension Check Quiz}
\begin{enumerate}
	\item What is the term for the act of controlling a person's thoughts, actions, and emotions by applying intrusive manipulation to the internal information processing of the brain, not for the individual's benefit, but for \textbf{the benefit of a third party}?
	\item What phenomenon is described in these notes as the decision-making authority for applying an overwhelming majority of citizens' strongly held ideology or belief to concrete situations becoming concentrated in a single political power?
	\item What dangerous impulse is triggered when 'what is right' becomes the social mainstream, causing the society to attempt the \textbf{thorough exclusion} of different views or actions?
	\item What concept, referring to the \textbf{fundamental principle} of an ideology or religion, is argued to be dangerous when the authority to interpret and apply it to specific situations is monopolized by a political power?
	\item What term refers to the power to monopolize the interpretation of American democracy, likened to the Roman Pope's historical monopoly on interpreting the Bible, and is attributed to the modern US President?
	\item What attitude is expected to prevent a nation from making extreme decisions, such as engaging in war, by ensuring the majority of citizens are not bound by a single standard of judgment and instead hold various ideas and beliefs?
	\item What technique is needed to \textbf{overwrite the manipulated brain information with different information}, as merely informing a cult member of the deception is insufficient?
	\item The thought pattern of a person who is completely free from worldly desires and has transcended the social judgments (good and evil) of this world is expressed in these notes as the 'logic of \_\_\_\_'. Fill in the blank.
	\item What concept serves as the basis for the idea that judging something, such as good and evil, as 'right' is itself a result of manipulation, having been provided by the ruling power of the time?
	\item What psychological tendency held by the public is said to create a situation in Japanese Diet elections where hereditary candidates are overwhelmingly favored compared to those from ordinary families?
	\item Why are groups that advocate for vague, but pleasant-sounding doctrines, such as 'world peace' or 'the future of the universe,' considered dangerous?
	\item What \textbf{excessive concentration} of power, noted since the time of the Crusades, is cited as a cause for religion deviating from its inherently peaceful nature to incite terrorism and war?
	\item In contrast to brainwashing, whose benefit should the essence of education serve?
	\item According to these notes, what is the relationship between achieving complete freedom from the 'logic of this world' and being a socially 'good person'?
	\item What is the target that receives the benefit, which is specified to clarify that the purpose of brainwashing is 'not for \textbf{the benefit of the individual}'?
\end{enumerate}

\subsubsection*{Answer Key}
1. Brainwashing, 2. Centralization of Interpretation Authority, 3. Strongly believing in 'what is right', 4. Principle, 5. Interpretation Authority, 6. Diverse Values, 7. Self-De-brainwashing Technique, 8. The Other World, 9. Social Judgment, 10. Brainwashed Brand Consciousness, 11. Vague, neatly packaged doctrines are often promoted by cults, 12. Centralization of the authority to interpret the principle for concrete application, 13. The benefit of the individual, 14. No relation, 15. The benefit of a third party

\begin{thebibliography}{99}
	\bibitem{toma} Tomabechi, H., \textit{Self-Defense Against Brainwashing}, Saisai Books, October 2003.
\end{thebibliography}

\end{document}