\documentclass[dvipdfmx, autodetect-engine, aspectratio=169, 10.5pt]{beamer}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[english]{babel}

\usetheme{Boadilla}
\usetheme{Marburg}
\usecolortheme{orchid}
\usefonttheme{professionalfonts}

\title{
Log.
}

\author{
Author
}

\date{Nov. 2025}

\begin{document}
\maketitle

\section{November 1, 2025 (Sat)}
\begin{frame}{November 1, 2025 (Sat)}
	\tiny

	\textbf{Fact}
	\begin{itemize}
		\item The morning was spent creating a resume, collaborating with Gemini to produce a high-quality result.
		\item An afternoon visit to a bookstore in search of generative AI life-hack books yielded no suitable finds.
		\item In the evening, met a friend for South Indian food in a bustling downtown area, crowded due to the Halloween season.
		\item A new business name, "Quant Marketing Lab," was established for personal projects.
	\end{itemize}

	\textbf{Event (Impression)}
	\begin{itemize}
		\item A strong sense of awe at the potential of generative AI, realizing its possibilities through co-creation.
		\item Navigating the downtown crowd was physically exhausting, but a sense of relief came upon reaching the restaurant and enjoying the meal.
		\item The walk home, spent discussing books with a friend, sparked a renewed motivation for reading.
	\end{itemize}

	\textbf{Reflection (Analysis)}
	\begin{itemize}
		\item A desire to master AI is growing stronger daily, bringing with it a feeling akin to impatience.
		\item The urban noise and crowds are draining; a reaffirmation that performance is best in a quiet environment.
		\item The rapid pace of AI evolution raises concerns about the long-term viability of current learning.
	\end{itemize}

	\textbf{Insight}
	\begin{itemize}
		\item Generative AI is not just a tool, but a creative partner that enhances the quality of thought.
		\item Learning is not "training to produce results," but "continuous updating to adapt to change."
		\item The new business name, "Quant Marketing Lab," provides a clear direction for intellectual activities.
	\end{itemize}

	\textbf{Next Step}
	\begin{itemize}
		\item Continue practical collaboration with generative AI for at least six months to refine operational skills and ideation.
		\item Tomorrow will be a dedicated reading day, progressing through "Childhood's End" and other generative AI books on hand.
		\item Secure quiet time and space to regain depth of thought.
	\end{itemize}
\end{frame}

\section{November 2, 2025 (Sun)}
\begin{frame}{November 2, 2025 (Sun)}
	\tiny

	\textbf{Fact}
	\begin{itemize}
		\item The entire day was spent in deep work at home.
		\item Developed a script to automate the generation of MBA lecture transcripts.
		\item Built a system using OpenAI Whisper for transcription, feeding into a prompt template to auto-generate LaTeX notes.
		\item A 12-hour stretch of deep work from noon until night, without breaks.
		\item The morning included the family routine of a fast-food breakfast; the 2-year-old daughter showed interest in the computer.
	\end{itemize}

	\textbf{Event (Impression)}
	\begin{itemize}
		\item A sense of wonder at how well the script performed, automating tasks and producing high-quality output.
		\item A feeling of fulfillment derived from self-directed efficiency, rather than external instructions.
		\item The sight of my daughter trying to touch the computer was endearing, a moment of warmth amidst the busy day.
	\end{itemize}

	\textbf{Reflection (Analysis)}
	\begin{itemize}
		\item A reaffirmation of the tendency to work to the point of exhaustion once focus is engaged.
		\item Realization that mastering AI is less about operation and more about providing high-quality data and instructions.
		\item While efficiency increases, the need for one's own creative thought is also called into question.
	\end{itemize}

	\textbf{Insight}
	\begin{itemize}
		\item Experienced firsthand the complementary relationship between AI and humans, each fulfilling different roles.
		\item "Coexistence with AI" is also a challenge of human intention and structural design.
		\item The natural coexistence of technology and family life holds clues for the future of work.
	\end{itemize}

	\textbf{Next Step}
	\begin{itemize}
		\item To expand the scope of collaboration with generative AI, read specialized books on its application.
		\item Consciously integrate breaks during long work sessions to establish a rhythm of focus and recovery.
		\item Refine this system into a versatile workflow that can be reused for other learning and business tasks.
	\end{itemize}
\end{frame}


\section{November 3, 2025 (Mon)}
\begin{frame}{November 3, 2025 (Mon)}
	\tiny

	\textbf{Fact}
	\begin{itemize}
		\item A quietly busy day spent creating MBA lecture notes with generative AI.
		\item A sense of efficient learning emerged as methods for data handling and prompt creation became more refined.
		\item A plan to share the lecture notes with the company, aiming to elevate the team's collective knowledge.
	\end{itemize}

	\textbf{Event (Impression)}
	\begin{itemize}
		\item A sense of accomplishment at moments of effective prompting.
		\item The satisfaction of the learning process becoming more systematic and internalized.
		\item A realization that being observed by others can enhance motivation and maintain quality.
	\end{itemize}

	\textbf{Reflection (Analysis)}
	\begin{itemize}
		\item Realized that quiz-style outputs shift passive listening into active inquiry.
		\item Recognized a personal trait: concentration and understanding deepen when learning is structurally designed.
	\end{itemize}

	\textbf{Insight}
	\begin{itemize}
		\item Crafting precise instructions for AI doubles as training for one's own thought organization.
		\item Externalizing the learning structure via AI is an effective way to train the mind efficiently.
	\end{itemize}

	\textbf{Next Step}
	\begin{itemize}
		\item Learn more advanced applications of generative AI to utilize it at a deeper level.
		\item Invest time not only in the MBA topics but in the study of generative AI itself to boost intellectual productivity.
	\end{itemize}
\end{frame}

\section{November 4, 2025 (Tue)}
\begin{frame}{November 4, 2025 (Tue)}
	\tiny

	\textbf{Fact}
	\begin{itemize}
		\item Started the day slowly after a late night, securing about 8 hours of sleep.
		\item Ate bakery bread, bought by my wife, for brunch; it was delicious, even for the second day in a row.
		\item Held a meeting with the marketing team at 12:30 PM.
		\item Organized MBA lecture videos and created corresponding notes.
		\item Development work involved building a historical table for real-time data, utilizing AWS Lambda and EventBridge.
		\item The evening was spent reading Schumpeter, reflecting on "creative destruction" and "new combinations."
		\item Prepared and ate steamed chicken for dinner, heading to bed around 9 PM.
	\end{itemize}

	\textbf{Event (Impression)}
	\begin{itemize}
		\item A day defined by a sense of fulfillment and calm, allowing for deep, focused work in a quiet environment.
		\item A comfortable feeling as natural questions emerged while creating MBA notes, fostering a sense of inquiry.
		\item Small joys, like the delicious bread, coexisted with intellectual fulfillment.
		\item A strong sense of both accomplishment and curiosity.
	\end{itemize}

	\textbf{Reflection (Analysis)}
	\begin{itemize}
		\item Immersing in long, focused work felt true to character.
		\item At the same time, a sense of needing to balance this introspection with external interaction arose.
		\item The process of giving form to knowledge, not just absorbing it, is the true source of fulfillment.
	\end{itemize}

	\textbf{Insight}
	\begin{itemize}
		\item Reading Schumpeter provided insight into the true flow of innovation: "destruction $\rightarrow$ new combination $\rightarrow$ creation."
		\item An interest in understanding capitalism from a non-Marxist perspective deepened, sparking a desire to grasp the world's mechanisms more broadly.
		\item Learning thrives in a cycle of quiet reflection and practice.
	\end{itemize}

	\textbf{Next Step}
	\begin{itemize}
		\item Attend the new MBA lectures starting tomorrow, using the note-taking process to deepen reflection.
		\item Organize administrative tasks (company messages, mail) to approach new learning with a clear mind.
	\end{itemize}
\end{frame}

\section{November 5, 2025 (Wed)}
\begin{frame}{November 5, 2025 (Wed)}
	\tiny

	\textbf{Fact}
	\begin{itemize}
		\item Woke at 4 AM and dove into a full day of development work.
		\item Shared accumulated MBA knowledge memos internally, aiming to elevate the team's skill level.
		\item The completed BI dashboard catalog was shared with employees, receiving a positive response.
		\item A request to develop a new marketing system came during an afternoon meeting; assigned as the lead developer.
		\item Recognizing the high-load state, took a deliberate trip to a bookstore after work to buy a textbook on time-series analysis.
	\end{itemize}

	\textbf{Event (Impression)}
	\begin{itemize}
		\item The day began with a vivid dream about receiving a large sum of money.
		\item A deep satisfaction from having the work's "value" recognized, beyond simple task completion.
		\item A conscious "disconnection" by physically stepping away from the PC, acknowledging the state of overwork.
	\end{itemize}

	\textbf{Reflection (Analysis)}
	\begin{itemize}
		\item The "flow state" that lasted from the morning, while immersive, also brought an objective concern about personal capacity.
		\item When the new request arrived, the immediate feeling was concern over capacity rather than excitement for the challenge—a sign of continuous high load.
		\item The pressure that remains even after tasks are delegated is a reminder that responsibility isn't measured by volume alone.
	\end{itemize}

	\textbf{Insight}
	\begin{itemize}
		\item Realized that results born from high concentration (the dashboard) quickly return as new, larger expectations (the new system).
		\item A physical change of scenery (bookstore) combined with a new, related intellectual stimulus (time-series analysis) can be an effective reset for mental saturation.
	\end{itemize}

	\textbf{Next Step}
	\begin{itemize}
		\item The first step is to apply the insights from the time-series analysis textbook to the new marketing system's development.
		\item In parallel, explore its application to stock analysis, fostering pure intellectual curiosity and broadening its scope.
	\end{itemize}
\end{frame}

\section{November 6, 2025 (Thu)}
\begin{frame}{November 6, 2025 (Thu)}
	\tiny

	\textbf{Fact}
	\begin{itemize}
		\item The morning involved fixing a bug in an analysis dashboard, followed by a hurried preparation to go out.
		\item Met a friend for an unusual foreign dish (a stew) in the city, followed by coffee.
		\item Purchased several specialized books: quantum computing, stochastic differential equations, and generative AI in investing.
		\item Visited company offices in multiple locations, receiving a company logo T-shirt.
		\item Attended an evening lecture on category theory by a mathematician at a location in the city, getting a book signed and a brief chat afterward.
	\end{itemize}

	\textbf{Event (Impression)}
	\begin{itemize}
		\item While the conversation was enjoyable, the "novelty and flavor" of the foreign dish itself left a strong sensory impression.
		\item The brief conversation with the author after the lecture is remembered as a moment of intellectual stimulation.
	\end{itemize}

	\textbf{Reflection (Analysis)}
	\begin{itemize}
		\item Direct contact with an expert evokes pure "intellectual excitement" and simultaneously a strong, introspective desire to "study more."
		\item The morning rush is noted as a simple fragment of fact, having no lasting impact on the day's mood.
	\end{itemize}

	\textbf{Insight}
	\begin{itemize}
		\item A reaffirmation that this intellectual curiosity is not event-driven but constantly directed toward foundational mathematics, like diffusion models or general relativity.
		\item Awareness of the need to consciously manage this intake, evidenced by deferring a purchase (a Riemannian geometry text) to avoid "intellectual indigestion."
	\end{itemize}

	\textbf{Next Step}
	\begin{itemize}
		\item Move forward with reading the newly acquired specialized books, particularly stochastic differential equations, to deepen the mathematical understanding of these fields.
	\end{itemize}
\end{frame}

\section{November 7, 2025 (Fri)}
\begin{frame}{November 7, 2025 (Fri)}
	\tiny

	\textbf{Fact}
	\begin{itemize}
		\item Went out with my wife to a government office to renew public support documents.
		\item Paused at a park en route, introducing my wife to a dark beer, which she seemed to enjoy.
		\item My wife is in a cyclically high-energy mental state and spoke of wanting to start a YouTube channel for her art.
		\item After returning home and picking up our daughter, met a friend locally, visiting a pub and a sushi restaurant, and drinking alcohol for the first time in six months.
		\item The consequence of drinking was feeling unwell into the next morning.
	\end{itemize}

	\textbf{Event (Impression)}
	\begin{itemize}
		\item A sense of "accomplishment" from completing a pending administrative task, lifting a mental burden.
		\item A quiet satisfaction in sharing a peaceful moment in the park, and in my wife finding a new beverage she enjoys.
	\end{itemize}

	\textbf{Reflection (Analysis)}
	\begin{itemize}
		\item Regarding my wife's new motivation, there's an equal mix of a desire to support her and "anxiety," given the understanding of her mental biorhythms.
		\item Having felt apologetic about inviting a friend to my local area, it was a pleasant surprise to find that the friend genuinely enjoyed the place.
	\end{itemize}

	\textbf{Insight}
	\begin{itemize}
		\item After six months without alcohol, this experience clearly reconfirmed a physical incompatibility with it.
		\item The optimal support for my wife during her energetic periods is "observation" and respecting her rhythm, rather than active intervention.
	\end{itemize}

	\textbf{Next Step}
	\begin{itemize}
		\item Continue to support my wife's ambitions in a way that respects her autonomy, without excessive interference.
		\item Maintain the decision to "absolutely not drink" alcohol, based on this clear physical feedback.
	\end{itemize}
\end{frame}

\section{November 8, 2025 (Sat)}
\begin{frame}{November 8, 2025 (Sat)}
    \tiny

    \textbf{Fact}
    \begin{itemize}
        \item A small amount of alcohol last night led to a hangover this morning, though recovery was complete by the afternoon.
        \item Attended a regular appointment at the clinic to continue prescriptions.
        \item Upon learning the attending doctor will be moving to a different location as hospital director next year, expressed the intention to continue seeing that same doctor.
        \item Finished reading a textbook on "English Learning with Generative AI" and a separate book on "High-Frequency Trading."
        \item In the evening, reading of "Childhood's End" continued, reaching the story's climax.
    \end{itemize}

    \textbf{Event (Impression)}
    \begin{itemize}
        \item The afternoon, post-recovery, was spent focused on reading, bringing a sense of intellectual fulfillment.
    \end{itemize}

    \textbf{Reflection (Analysis)}
    \begin{itemize}
        \item Finishing the AI how-to book brought an awareness—and impatience—that "without practice, there is no retention," a core tenet of a personal learning style.
        \item The decision to follow the doctor, even if it requires changing clinics, stems not only from long-term "trust" but also from the "potential for future collaboration" as the doctor takes on a management role.
    \end{itemize}

    \textbf{Insight}
    \begin{itemize}
        \item Experiencing a distinct hangover from a minimal amount of alcohol served as clear physical evidence, reinforcing yesterday's conclusion that alcohol is incompatible with this constitution.
        \item There is a clear need to "accelerate" intellectual activities, which now requires "investing" in paid generative AI services beyond the limitations of free tiers.
    \end{itemize}

    \textbf{Next Step}
    \begin{itemize}
        \item Put the concepts from the generative AI textbook into practice by actively using prompts and other hands-on methods.
        \item Move forward with evaluating and subscribing to a paid generative AI plan as an investment in intellectual productivity.
    \end{itemize}
\end{frame}

\end{document}